### 2013-07-18 doc/dissertation/document/chapters/parallel_mc/parallel_mc.tex
updating figure captions in subdomain monte carlo section

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_strong_subdomain_ms_time.pdf}
  \end{center}
  \caption{\textbf{Strong scaling total wall time with multiple sets
      and subdomain Monte Carlo.} \textit{The subdomain Monte Carlo
      solver improves the parallel efficiency and therefore time to
      solution by eliminating all parallel communication during the
      Monte Carlo solve.}}
  \label{fig:titan_strong_subdomain_ms_time}
\end{figure}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_strong_subdomain_ms.pdf}
  \end{center}
  \caption{\textbf{Strong scaling absolute efficiency for with
      multiple sets and subdomain Monte Carlo.} \textit{The subdomain
      Monte Carlo solver improves the parallel efficiency and
      therefore time to solution by eliminating all parallel
      communication during the Monte Carlo solve.}}
  \label{fig:titan_strong_subdomain_ms}
\end{figure}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_weak_subdomain_ms_time.pdf}
  \end{center}
  \caption{\textbf{Weak scaling total wall time with multiple sets
      and subdomain Monte Carlo.} \textit{The subdomain Monte Carlo
      solver improves the parallel efficiency and therefore time to
      solution by eliminating all parallel communication during the
      Monte Carlo solve.}}
  \label{fig:titan_weak_subdomain_ms_time}
\end{figure}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_weak_subdomain_ms.pdf}
  \end{center}
  \caption{\textbf{Weak scaling absolute efficiency for with
      multiple sets and subdomain Monte Carlo.} \textit{The subdomain
      Monte Carlo solver improves the parallel efficiency and
      therefore time to solution by eliminating all parallel
      communication during the Monte Carlo solve.}}
  \label{fig:titan_weak_subdomain_ms}
\end{figure}

>>>>

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_strong_subdomain_ms_time.pdf}
  \end{center}
  \caption{\textbf{Strong scaling total wall time with multiple sets
      and subdomain Monte Carlo.} \textit{Adding multiple sets has in
      general a negative effect on the wall time as was observed for
      the case with full Monte Carlo transport.}}
  \label{fig:titan_strong_subdomain_ms_time}
\end{figure}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_strong_subdomain_ms.pdf}
  \end{center}
  \caption{\textbf{Strong scaling absolute efficiency for with
      multiple sets and subdomain Monte Carlo.} \textit{Increased wall
      times from adding parallel reduction operations for multiple
      sets reduces parallel scalability at lower core counts but gives
      a higher efficiency at the strong scaling wall.}}
  \label{fig:titan_strong_subdomain_ms}
\end{figure}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_weak_subdomain_ms_time.pdf}
  \end{center}
  \caption{\textbf{Weak scaling total wall time with multiple sets and
      subdomain Monte Carlo.} \textit{The addition of the set tally
      reduction is significant with cost of the reduction observed as
      core count grows.}}
  \label{fig:titan_weak_subdomain_ms_time}
\end{figure}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_weak_subdomain_ms.pdf}
  \end{center}
  \caption{\textbf{Weak scaling absolute efficiency for with multiple
      sets and subdomain Monte Carlo.} \textit{Weak scaling
      efficiencies are not improved at large core counts when multiple
      sets are added.}}
  \label{fig:titan_weak_subdomain_ms}
\end{figure}
